Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-09-28 review_responses.tex

\noindent\textbf{Response:}
This is a helpful suggestion, and we have made the switch from $x$ and $t$ to $x_{\theta}$ and $x_0$ throughout the manuscript.

\subsection{\textbf{R4.2} Optimal Targets}
\noindent\textbf{Review:}
You mentioned "There is no optimal or correct version of an 8-bit snare sound".
This statement is true when you are given only the text description of the sound. However, if you have the target sound $x_0$  the target sound itself is "correct", isn't it? So your hypothesis only holds if you don't have the target sound but the text description, am I understanding it correctly?\\

\noindent\textbf{Response:}
The original statement referred to how realistically in sound-design, a "correct" solution rarely exists due to our subjective experience of sound. To reduce confusion, the section has been rephrased as follows:
\begin{displayquote}
    Moreover, the ``correct'' solution may not exist in a strict sense: depending on the artistic goal, multiple parameter settings may yield acceptable or even preferable outputs.  In the following sections we will discuss the various components of sound-matching, the subjectivity of ``correct'' solutions, and important issues in the field.
\end{displayquote}

\subsection{R4.3 Hearing Tests}
\label{}
\noindent{\textbf{Review:}}
Also, in the blinded hearing test, the two listeners are the authors, it seems a bit too biased to me. Not sure how difficult is it to add one more listener, but I believe having an extra sound engineer/musician who is not one of the author would yield a more convincing listening results.
\\
\noindent{\textbf{Response:}}
The listening tests were done without use of any labels or previous exposure to outputs, which we believe minimizes the risk of bias. Unfortunately, adding another listener was not possible given the allotted time for the revisions. If the reviewer feels that this is necessary, it can be done for the next round of reviews.

### 2025-09-28 sections/background_related.tex
Updates from Overleaf

\subsubsection{Joint-Time Frequency Spectrum}
Recent works have focused on the limitations of parameter and spectral loss functions in sound-matching~\cite{vahidi2023mesostructures,uzrad2024diffmoog}, seeking to create more effective general solutions for the comparison of audio. 
Noting the aforementioned weaknesses of comparing STFT spectrograms\todo{you discussed loudness only and not misalignments}, Vahidi \textit{et al.} proposed differentiable Joint-Time Frequency Scattering (\gls{JTFS})~\cite{anden2015joint} as an alternative to spectrogram loss in sound-matching, and showed improved performance in sound-matching with differentiable chirplet synthesizers~\cite{vahidi2023mesostructures}. JTFS is the result of the application of a 2D wavelet transformation to the time-frequency representation of a signal~\cite{anden2015joint} and has been reported as more sensitive to mesostructural features such \todo{list}~\cite{vahidi2023mesostructures}.

@@

\subsection{In-Domain versus Out-of-Domain}
\label{sec:in-domain}
The choice of domain depends on whether we want to use the same synthesizer for the target and output sounds, the scenario that is called \textit{in-domain}, or have target sounds that came from sources other than the synthesizer, or \textit{out-of-domain}. To paraphrase the description given by Masuda \textit{et al.}~\cite{masuda2021soundmatch}, if $g$, the synthesizer of choice, can accurately replicate the target sound $\xzero$, or put differently, if $\xzero$ itself is an output of $g$, then the sound-matching task is \textit{in-domain}. If $\xzero$ is not an output of $g$, then the sound-matching task is \textit{out-of-domain}. In-domain tasks in general are simpler, and often there is a guarantee that there is a correct answer to the sound-matching problem, particularly if the goal is accurate replication of the sound. If the target sound is out-of-domain, replication is not guaranteed, and the goal becomes the \textit{imitation} of some aspect of sound.

@@

\subsection{Supvervised versus Direct Optimization}
\label{sec:optimization}

>>>>

\subsubsection{Joint-Time Frequency Spectrum}
Recent works have focused on the limitations of parameter and spectral loss functions in sound-matching~\cite{vahidi2023mesostructures,uzrad2024diffmoog}, seeking to create more effective general solutions for the comparison of audio. 
Noting the weaknesses of comparing STFT spectrograms (such as alignment and loudness distances), Vahidi \textit{et al.} proposed differentiable Joint-Time Frequency Scattering (\gls{JTFS})~\cite{anden2015joint} as an alternative to spectrogram loss in sound-matching, and showed improved performance in sound-matching with differentiable chirplet synthesizers~\cite{vahidi2023mesostructures}. JTFS is the result of the application of a 2D wavelet transformation to the time-frequency representation of a signal~\cite{anden2015joint} and has been reported as more sensitive to \textit{mesostructural} features such as melody, syncopation, and textural
contrast~\cite{vahidi2023mesostructures}.

@@

\subsection{In-Domain Versus Out-of-Domain}
\label{sec:in-domain}
The choice of domain depends on whether we want to use the same synthesizer for the target and output sounds, the scenario that is called \textit{in-domain}, or have target sounds that came from sources other than the synthesizer, or \textit{out-of-domain}. To paraphrase the description given by Masuda \textit{et al.}~\cite{masuda2021soundmatch}, if $g$, the synthesizer of choice, can accurately replicate the target sound $\xzero$, or put differently, if $\xzero$ itself is an output of $g$, then the sound-matching task is \textit{in-domain}. If $\xzero$ is not an output of $g$, then the sound-matching task is \textit{out-of-domain}. In-domain tasks in general are simpler, and often there is a guarantee that there is a correct answer to the sound-matching problem, particularly if the goal is accurate replication of the sound. If the target sound is out-of-domain, replication is not guaranteed, and the goal becomes the \textit{imitation} of some aspect of sound.

@@

\subsection{Supvervised Versus Direct Optimization}
\label{sec:optimization}

### 2025-09-28 sections/summary_weakness_conclusion.tex
Updates from Overleaf

\textbf{Q1}: To what extent do automatic evaluation metrics agree with manual listening tests? 
\\We see somewhat consistent results between the rankings assigned by manual hearing tests (which we take as the ground truth), and automatic measures of P-Loss and MSS. With the exception of P-Loss in \BPNoise{} narrowly selecting a different spectrogram based loss, all measures of performance selected the same top performer. However, given the simplicity of our programs and the occasional deviations, we cannot conclude that these automatic measures are substitutes for human hearing tests. As many previous works have done\todo{cite}, the use of MSS and/or P-Loss as general loss functions does seem appropriate, however, we advise the use of listening tests or custom made loss functions for more specific analysis.

>>>>

\textbf{Q1}: To what extent do automatic evaluation metrics agree with manual listening tests? 
\\We see somewhat consistent results between the rankings assigned by manual hearing tests (which we take as the ground truth), and automatic measures of P-Loss and MSS. With the exception of P-Loss in \BPNoise{} narrowly selecting a different spectrogram based loss, all measures of performance selected the same top performer. However, given the simplicity of our programs and the occasional deviations, we cannot conclude that these automatic measures are substitutes for human hearing tests. As many previous works have done (see Table~\ref{tab:summary}, the use of MSS and/or P-Loss as general loss functions does seem appropriate, however, we advise the use of listening tests or custom made loss functions for more specific analysis.
